Title

### 2024-01-22 Notes/fall_recap.tex
Added Quarto document with semiparametric constraint simulation.

The challenge with working with this class is the $\beta$ coefficients. These
are functional coefficients and so it is difficult for me to understand how to 
show that a particular class is optimal.

>>>>

The challenge with working with this class is the $\beta$ coefficients. These
are functional coefficients and so it is difficult for me to understand how to 
show that a particular class is optimal. Dispite this difficulty, we were able 
to show that the proposed estimator is not optimal via simulation. When this 
estimator was compared to other estimators in Table~\ref{eq:class}, it did not 
perform the best when the segments were unbalanced and the estimating function 
was nonlinear. This is shown in Table~\ref{tab:unbalanced}

\begin{table}[ht!]
  \caption{True Values: $\theta = 10$, $\rho = 0.5$. This simulation assesses 
  the bias and standard deviation (SD) of different estimators of the function 
$\theta = E[Y_1^2 Y_2]$ where $Y_1 = x + \varepsilon_1$, $Y_2 = \beta + x + 
\varepsilon_2$, $x \perp (\varepsilon_1, \varepsilon_2)$, and 
$(\varepsilon_1, \varepsilon_2)$ come from a mean zero bivariate normal 
distribution with unit variance and covariance of $\rho$. This simulation uses 
a sample size of $N = 1000$ and $B = 3000$ Monte Carlo simulations. Each 
observation has the following independent probabilities of landing into a 
respective segment: $\pi_{11} = 0.2$, $\pi_{10} = 0.4$, $\pi_{01} = 0.1$, and
$\pi_{00} = 0.3$. The columns of Tstat and P-value give the test statistic and
p-value from a two sample test for unbiasedness.}
  \label{tab:unbalanced}
  \centering
  \begin{tabular}[t]{lrrrr}
    \toprule
    Algorithm & Bias & SD & Tstat & P-value\\
    \midrule
    Oracle & 0.007 & 0.529 & 0.741 & 0.229\\
    CC & 0.036 & 1.190 & 1.667 & 0.048\\
    IPW & 0.029 & 1.372 & 1.170 & 0.121\\
    $\hat \theta_{prop}$ & 0.004 & 0.694 & 0.292 & 0.385\\
    $\hat \theta_{c}$ & 0.007 & 0.670 & 0.582 & 0.280\\
    $\hat \theta_{\delta}$ & 0.018 & 0.675 & 1.478 & 0.070\\
    \bottomrule
  \end{tabular}
\end{table}
